Deciphering enhancer rules underlying early human neuronal and neural crest development.

### 2025-04-02 manuscript.tex
Finalize figures.

\begin{figure}[b]
  \ContinuedFloat
  \caption*{\rule{\linewidth}{0.4pt}}
  \caption{
    (Continued) \textbf{g}, UMAP based on gene expression profiles of organoid (top; UMAP axis 1 and 2 shown) and embryo (bottom; UMAP
    axis 2 and 3 shown) for neuronal progenitor subcluster along with the expression of indicated genes in red-green-blue
    color scale. \textbf{h}, UMAP based on gene expression profiles in organoid (top left) and embryo (top right) colored by
    cell cycle phase identity and quantification of percentage of each cell for each cell cycle phase stratified by cell
    type in the organoid (bottom left) and embryo (bottom right). \textbf{i}, Average gene expression level in
    $log_{2}(CPM)$
    (dot color) and fraction of cells expressing the gene (dot size) per cell state, defined by topic modeling, for organoid
    cells (top) and embryo cells (middle) and motif enrichment level as normalized enrichment score (NES; dot color) and
    number of regions enriched for the motif (dot size) per topic (x-axis) and motif (y-axis; bottom). PVM/MIC: perivascular
    microphage/microglia.
  }
\end{figure}

>>>>

\begin{figure}[b!]
  \ContinuedFloat
  \caption*{\rule{\linewidth}{0.4pt}}
  \caption{
    (Continued) \textbf{g}, UMAP based on gene expression profiles of organoid (top; UMAP axis 1 and 2 shown) and embryo (bottom; UMAP
    axis 2 and 3 shown) for neuronal progenitor subcluster along with the expression of indicated genes in red-green-blue
    color scale. \textbf{h}, UMAP based on gene expression profiles in organoid (top left) and embryo (top right) colored by
    cell cycle phase identity and quantification of percentage of each cell for each cell cycle phase stratified by cell
    type in the organoid (bottom left) and embryo (bottom right). \textbf{i}, Average gene expression level in
    $log_{2}(CPM)$
    (dot color) and fraction of cells expressing the gene (dot size) per cell state, defined by topic modeling, for organoid
    cells (top) and embryo cells (middle) and motif enrichment level as normalized enrichment score (NES; dot color) and
    number of regions enriched for the motif (dot size) per topic (x-axis) and motif (y-axis; bottom). PVM/MIC: perivascular
    microphage/microglia.
    Color scales for RGB scatter plots are as follows (in Log(CPM)). 
    For organoid:
    ARX [0, 1.5],
    NKX2-2 [0, 1.5],
    PAX6 [0, 1.5],
    IRX3 [0, 1.0],
    ZIC1 [0, 1.5],
    GDF7 [0, 1.5],
    SIX3 [0, 1.5],
    EMX2 [0, 1.5],
    FOXG1 [0, 0.8],
    BARHL1 [0, 1.0],
    EN1 [0, 1.5],
    HOXB3 [0, 1.5],
    SOX2 [0, 1.5],
    ASCL1 [0, 1.5],
    ISL1 [0, 1.5],
    GAD1 [0, 0.8],
    UNXC [0, 0.8],
    GATA2 [0, 0.8],
    GRHL2 [0, 1.5],
    ZEB2 [0, 3.0],
    SOX10 [0, 0.8],
    NEUROD1 [0, 1.5],
    PAX2 [0, 1.5],
    TWIST1 [0, 1.5]
    For embryo:
    ARX [0, 1.5],
    NKX2-2 [0, 1.5],
    PAX6 [0, 1.5],
    IRX3 [0, 1.5],
    ZIC1 [0, 1.5],
    GDF7 [0, 1.5]
    SIX3 [0, 1.5],
    EMX2 [0, 1.5],
    FOXG1 [0, 0.8],
    BARHL1 [0, 1.5],
    EN1 [0, 1.5],
    HOXB3 [0, 1.5],
    SOX2 [0, 1.5],
    ASCL1 [0, 1.5],
    ISL1 [0, 1.0]
    GAD1 [0, 0.8],
    UNXC [0, 0.8],
    GATA2 [0, 0.8]
    GRHL2 [0, 1.5],
    ZEB2 [0, 3.0],
    SOX10 [0, 0.8]
    NEUROD1 [0, 1.5],
    PAX2 [0, 1.5],
    TWIST1 [0, 2.0]
  }
\end{figure}
